### 2017-05-29 sheets/basis-3/sheet-basis-3.tex

to a functor in such a way that $(\epsln)_{B \in \cat{B}}$ is a natural

@@

                    Using this commutativity for $\eta$ we obtain our goal.

@@

@@

            $F$ is essentially surj. on obj. so $\forall B \in \cat{B}.\, \exists A \in \cat{A}.\, F(A) \iso B$.
            We denote by $h(A, B) \from F(A) \to B$ this isomorphism.
            For each $B \in \cat{B}$ we define $G(B)$ such that $F(G(B)) \iso B$ under $h(G(B), B)$ and $\epsln_B\from F(G(B)) \to B := h(G(B), B)$.

@@

            We obtain $G(F(f)) = \eta_{A'} \circ f \circ \eta_A^{-1}$ because $F$ is faithfull.

>>>>

to a functor in such a way that $(\epsln_B)_{B \in \cat{B}}$ is a natural

@@

                    Using the naturality axiom for $\eta$ we obtain our goal.

@@

                    Let $A, A' \in \cat{A}$ and $g \from F(A) \to F(A')$.

@@

            For each $B \in \cat{B}$ the class of objects $A \in \cat{A}$ which fulfill $F(A) \iso B$ is non empty, because $F$ is essentially surjective on objects.
            We define $G(B)$ as such an $A$ using the axiom of choice.
            In addition we have an isomorphism $\epsln_B\from F(G(B)) \to B$.

@@

            We obtain $G(F(f)) = \eta_{A'} \circ f \circ \eta_A^{-1}$ because $F$ is faithful.
